### 2021-07-28 PrevAdjSurvey.tex

>>>>

Two scenarios fall under my Dirichlet Weights Simulation:

\begin{itemize}
    \item 8,000 individuals (groups of 1) with population prevalence 0.05\% and varying variance among the weights.
    \item 200 groups of 50 sampled with population prevalence 0.05\%, varying ICC, and varying variance among the weights.
\end{itemize}

The weight of each group is generated from a Dirichlet distribution with equal concentration parameters for all dimensions.

The positivity of each group is generated from a Beta distribution which achieves the specified mean and ICC.

As you predicted, the usual methods (Agresti-Coull and Clopper-Pearson) exhibit poor performance when there is high variance among the weights.

Dean and Pagano recommend an adjustment suggested by Korn and Graubard that I wasn’t sure how to apply in the context of my simulation, so it’s possible that this is a pessimistic assessment of those methods.

Let’s chat about these results and next steps early next week.

Thanks,

Damon
